\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\printindex

\begin{thebibliography}{00}
\bibitem{b1}Kozierok, C. M., Correa, C., Boatright, R. B., \& Quesnelle, J. (2014). Automotive Ethernet: The Definitive Guide. Intrepid Control Systems.

\bibitem{b2} Steinbach, T., Korf, F., \& Schmidt, T. C. (2011, September). Real-time Ethernet for automotive applications: A solution for future in-car networks. In 2011 IEEE International Conference on Consumer Electronics-Berlin (ICCE-Berlin) (pp. 216-220). IEEE.


\bibitem{b3} Han, S., \& Kim, H. (2016). On AUTOSAR TCP/IP performance in in-vehicle network environments. IEEE Communications Magazine, 54(12), 168-173.

\bibitem{b4} Matheus, K., \& Königseder, T. (2017). A Brief History of “Ethernet” (from a Car Manufacturer's Perspective). In Automotive Ethernet(pp. 1-29). Cambridge: Cambridge University Press. doi:10.1017/9781316869543.003 

\bibitem{b4_1}Matheus, K., \& Königseder, T. (2017). A Brief History of In-Vehicle Networking. In Automotive Ethernet(pp. 30-68). Cambridge: Cambridge University Press. doi:10.1017/9781316869543.004

\bibitem{b_4_2}Matheus, K., \& Königseder, T. (2017). The Physical Transmission of Automotive Ethernet. In Automotive Ethernet (pp. 102-188). Cambridge: Cambridge University Press. doi:10.1017/9781316869543.006

\bibitem{b5.0} Hank, P., Müller, S., Vermesan, O., \& Van Den Keybus, J. (2013, March). Automotive ethernet: in-vehicle networking and smart mobility. In 2013 Design, Automation \& Test in Europe Conference \& Exhibition (DATE) (pp. 1735-1739). IEEE.

\bibitem{b5} Krishnadas, S. (2016). Concept and Implementation of AUTOSAR compliant Automotive Ethernet stack on Infineon Aurix Tricore board.

\bibitem{b5_1}Kim, Y. (2011). Very low latency packet delivery requirements and problem statements. In IEEE 802.1 AVB Task Group Interim Meeting.

\bibitem{b_6_0}Bo, H., Hui, D., Dafang, W., \& Guifan, Z. (2010, May). Basic concepts on AUTOSAR development. In 2010 International Conference on Intelligent Computation Technology and Automation (Vol. 1, pp. 871-873). IEEE.

\bibitem{b_6_1}Wagner, M., Zobel, D., \& Meroth, A. (2014, September). Towards runtime adaptation in AUTOSAR: Adding Service-orientation to automotive software architecture. In Proceedings of the 2014 IEEE Emerging Technology and Factory Automation (ETFA) (pp. 1-7). IEEE.

\bibitem{b6} AUTOSAR Release 4.3.1, “Layered Software Architecture”, 08-Dec-2017. [Online]. Available: \url{https://www.autosar.org/fileadmin/user\_upload/standards/classic/4-3/AUTOSAR_EXP_LayeredSoftwareArchitecture.pdf}, [Accessed: 05-May-2021]. 

\bibitem{b7} AUTOSAR Release 4.3.1, “Specification of Ethernet Switch Driver,” 08-Dec-2017. [Online]. Available: \url{https://www.autosar.org/fileadmin/user_upload/standards/classic/4-3/AUTOSAR_SWS_EthernetSwitchDriver.pdf}. [Accessed: 11-May-2021].  

\bibitem{b8}AUTOSAR Release 4.3.1, “Specification of TCP/IP Stack”, 08-Dec-2017. [Online]. Available: \url{https://www.autosar.org/fileadmin/user_upload/standards/classic/4-3/AUTOSAR_SWS_TcpIp.pdf}. [Accessed: 13-May-2021].

\bibitem{b9} AUTOSAR Release 4.3.1. “Specification of Socket Adaptor”, 08-Dec-2017. [Online]. Available: \url{https://www.autosar.org/fileadmin/user_upload/standards/classic/4-3/AUTOSAR_SWS_SocketAdaptor.pdf}. [Accessed: 14-May-2021].

\bibitem{b10}Abdelhamid, A. Y. A. (2018). Evaluation of a Control Protocol for Testing an Automotive Ethernet TCP/IP Stack.

\bibitem{b11}Alliance, O. (2017). OPEN Alliance Automotive Ethernet ECU Test Specification. TC8 ECU, August, 23.

\end{thebibliography}